Fitting the Undetected: Light-curve Feature Estimation in the Presence of Non-detections

### 2013-03-29 tex/ms.tex
finished intro, discussion notes

\hogg{note to self: either merge in or delete the material below this line}

\joey{RRL end at 120 kpc in Sesar et al. paper}

\joey{discuss in context of: parameter estimation (amplitude / period), discovery (we're gonna find a lot more variable sources if we take the non-detections into account), and classification; lossiness}

\joey{let's make a point to stress variable discovery}

\joey{Numbers of LCs affected: Stripe 82, ASAS}

@@

What people can do, starting from the data-taking procedure.

limitations

>>>>

In what follows, we concentrate on parameter estimation---fitting of amplitudes and periods to noisy censored data%
---but because modeling, parameter estimation, discovery, and classification are intertwined,
this work has implications in all these areas.
For example, we often conclude that a star \emph{is} a periodic variable because parameter estimation delivers a solid period.
We often conclude that a star is a Mira or a RR Lyrae star because it's best-fit period or lightcurve shape is in some range.
For example, the valuable RR Lyrae catalog generated with \textsl{SDSS Stripe 82} data (CITE SESAR) classified stars
by performing parameter estimation and then cutting on derived parameters.
This study worked in the traditional mode of ignoring censored data, thereby limiting its ability to find the faintest
(and therefore most distant) RR Lyrae stars.
A model for the censored data might have extended the reach of this survey and led to new discoveries of Milky Way structure.
\hogg{Joey: add words here about your own variable-star catalog and what could be improved.}

@@

\hogg{This section should include limitations of what we have done:  We didn't vary all available model parameters.  Our code is slow.  We don't permit time dependence to the censoring model.  Our noise model is naive at best.}

\hogg{This section should return to the detection point and the promise of that.}

\hogg{This section should NOT be a summary of the paper:  That lives in the abstract!}
